### 2015-12-28 docs/ms_communitySynchrony.Rmd
updates discussion with community assembly and conclusions

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \usepackage{todonotes}
   - \doublespacing
   - \usepackage[document]{ragged2e}
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl

@@

@@

\normalsize{Andrew T. Tredennick\footnote{Correspondance: atredenn@gmail.com}\textsuperscript{1}, Claire de Mazancourt\textsuperscript{2}, Michel Loreau\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}

@@

\vspace{5em}

*Authorship*: ATT, CdM, and PBA designed the research, ATT performed the research, and ATT, CdM, ML, and PBA contributed to the analyses and interpretation of results. All authors contributed to writing the manuscript.

\renewcommand*{\thefootnote}{\arabic{footnote}}
\setcounter{footnote}{0}

@@

__Keywords__: synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, stability

<!-- \setlength{\parindent}{5ex} -->

@@

Discovering the mechanisms behind population fluctuations, and whether they are synchronous among species or not, is a long-standing goal of ecology.
One view is that density-dependent processes like interspecific competition lead to compensatory dyanmics [e.g., @Elton1942; @Tilman1988; @Ives1995].
An alternative view is that density-independent processes like environmental forcing drive population fluctuations and tend to synchronize dynamics of ecologically-similar species [@Strong1983; @Fischer2001].
Clearly, these forces are not mutually exclusive, and most research has focused on determining the relative strength of biotic and abiotic forcing on the synchrony of community dynamics [e.g., @Ives1995; @Klug2000; @Houlahan2007; @Mutshinda2009].
However, recent theory [@Loreau2008a] suggests that previous interpretations of time series have been impaired by a (1) faulty metric of synchrony that treated synchrony and asynchrony as binary states, (2) biased null expectations of species synchrony, and (3) the use of population abundances that are strongly influenced by lag effects to estimate immediate responses to the environment and competition.
Moreover, interspecific competition may actually synchronize, rather than de-synchronize, population dynamics [@Loreau2008a; @Loreau2010].

@@

where $\sigma_{r_{i}}$ is the temporal variance of species *i*'s per capita population growth rate ($r_i$) and $\sigma^{2}_{T}$ is the temporal variance of the aggregate community-level growth rate. 
The metric of @Loreau2008a makes clear that synchrony and asynchrony are not binary states, contrary to their common usage in the literature.
Rather, the synchrony of community dynamics lies along a continuum from perfect asynchrony ($\phi_r=0$) to perfect synchrony ($\phi_r=1$).
Thus, our focus should not be on whether or not (a)synchronous dynamics occur, but instead on the degree of (a)synchrony within a community and what process increase or decrease sychrony.

@@

where $\sigma^{2}_{c}$ is the temporal variance of per capita population growth rates due to regulation of community size (density-dependence), $\sigma^{2}_{e}$ is environmental variance, and $\sigma^{2}_{d}$ is demographic variance. *S* is the species richness of the focal community and *N* is the harmonic temporal mean of either the entire community (no subscript in numerator) or species *i* (with subscript in denominator). 
Their analysis isolates three main factors that drive species synchrony in competitive communities: (1) density-dependence via intra- and interspecific competition, (2) environmental fluctuations, and (3) demographic stochasticity.

@@

### Demographic stochasticity decreases synchrony
In communities where environmental forcing and community regulation by inter and intraspecific density-dependence are weak, species should fluctuate independently and community synchrony is expected to equal the inverse of the number of species in the community (1/*S*).
Such independent fluctuations are expected for per capita growth rates regardless of population sizes, whereas synchrony of percent cover should trend toward one (perfect synchrony) as population sizes increase and the effect of demographic stochasticity is diminished.
Our results conform to expectations: for each community except Arizona, community synchrony of per capita growth rates are approximately equal to 1/*S* when only demographic stochasticity is acting (Fig. 3; top panels, dark purple lines) and synchrony of percent cover starts at approximately 1/*S* and increases linearly as population sizes increase (Fig. 3; bottom panels, dark purple lines).
In the Arizona community, synchrony of per capita growth rates is approximately 1/*S* as expected, but synchrony of precent cover does not increase with population size (Fig. 3f).
This could indicate that intraspecific density-dependence is abnormally strong in the Arizona community, relative to the other communities we studied.
Strong intraspecific density-dependence for the two species in the Arizona community would limit population size regardless of landscape size.
Therefore, populations would not grow large enough to limit the desynchronizing effect of demographic stochasticity.
In other words, if there is no relationship between landscape size and population size due to strong density-dependence, the effect of demgographic stochasticity will not lessen.
TODO: CHECK MEAN COVER VERSUS LANDSCAPE SIZE FOR EACH COMMUNITY

@@

### Environmental fluctuations drive community synchrony
In large populations where interspecific interactions are weak, synchrony is expected to be driven exclusively by environmental fluctuations.
Under such conditions community synchrony should approximately equal the synchrony of species' responses to the environment.
We find that environmental fluctuations drive synchrony of per capita growth rates and plant percent cover in all five communities.
Removing environmental fluctuations consistently reduced synchrony (Fig. 3) and the synchrony of species environmental responses was a strong predictor of community synchrony ($\text{R}^2$ = 0.67; Fig. 4).
Likewise, removing interspecific interactions resulted in no discernable change in community synchrony of per capita growth rates (Fig. 2).
The lack of change indicates a strong correlation between species growing in polyculture (with interspecific interactions) and in monoculture (without interspecific interactions).
If we consider sychrony in monoculture to represent the synchrony of species' responses to the environment, then our results lead to only one conclusion: environmental fluctuations are the primary driver of community synchrony.
This is unsurprising since we know that species interactions are weak in these communities.
More surprising is that our results appear to be quite general: across five arid-to-subhumid grasslands community synchrony is almost soley due to environmental fluctuations since interspecific interactions are weak.
Can we generalize our results to a vast majority of plant communities?

A recent analysis of several biodiversity-ecosystem function experiments suggests our results are anomolous.
@Gross2014 found that temporal asynchrony among plant species in four experiments was driven by interspecific competition that counteracted the synchronizing effect of environmental fluctuations.
In fact, they found very weak correlations among species growin in polyculture and species growing in monoculture.
However, their results are based on experimentally-assembled communities that have coexisted for, at most, 11 years.
Thus, community assembly processes that can result in competitive exclusion may yet to have been realized and transient strong interspecific competition could be masking the synchronizing effects of the environment.
In contrast, the communities we studied consist of species that have coexisted for decades and have virtually zero niche overlap [@Chu2015].

@@

@@

pgr_plot <- ggplot(data=pgr_data, aes(x=(year+1900), y=pgr, color=color))+
              geom_line(alpha=0.25)+
                geom_point(size=2)+
              facet_grid(site~., scales = "free_y")+
              guides(color=FALSE)+
              ylab("Per Capita Growth Rate")+
              xlab("Year")+
              scale_color_manual(values = brewer.pal(12,"Paired"))+
              theme_bw()
full_plot <- grid.arrange(cover_plot, pgr_plot, ncol=2)
```

>>>>

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \usepackage{todonotes}
   - \doublespacing
   - \usepackage[document]{ragged2e}
   - \usepackage{color}
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl

@@

\begin{singlespace}

@@

\normalsize{Andrew T. Tredennick\textsuperscript{1}, Claire de Mazancourt\textsuperscript{2}, Michel Loreau\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}

@@

\textit{Authorship}: ATT, CdM, and PBA designed the research, ATT performed the research, and ATT, CdM, ML, and PBA contributed to the analyses and interpretation of results. All authors contributed to writing the manuscript.

\textit{Keywords}: synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, stability

\textit{Running Title}: Species synchrony in grasslands

\textit{Article Type}: Letter

\textit{Number of Words}: Abstract = ; Main Text =

\textit{Number of References}:

\textit{Number of Tables and Figures}:  Tables;  Figures

\textit{Corresponding Author}: Andrew Tredennick \\  
Address: Department of Wildland Resources and the Ecology Center, 5230 Old Main Hill, Utah State University, Logan, Utah 84322 USA \\
Phone: +1-970-443-1599 \\
Fax: +1-435-797-3796 \\
Email: atredenn@gmail.com

\end{singlespace}
\renewcommand*{\thefootnote}{\arabic{footnote}}
\setcounter{footnote}{0}

@@

<!-- \setlength{\parindent}{5ex} -->
\setlength{\parindent}{5ex}

@@

Discovering the mechanisms behind population fluctuations, and whether they are synchronous among species or not, is a long-standing goal of ecology.
One view is that density-dependent processes like interspecific competition lead to compensatory dyanmics [e.g., @Elton1942; @Tilman1988; @Ives1995].
An alternative view is that density-independent processes like environmental forcing drive population fluctuations and tend to synchronize dynamics of ecologically-similar species [@Strong1983; @Fischer2001].
Clearly, these views are not mutually exclusive, and most research has focused on determining the relative strength of biotic and abiotic forcing on the synchrony of community dynamics [e.g., @Ives1995; @Klug2000; @Houlahan2007; @Mutshinda2009].
However, recent theory [@Loreau2008a] suggests that previous interpretations of time series have been impaired by (1) a faulty metric of synchrony that treated synchrony and asynchrony as binary states, (2) biased null expectations of species synchrony, and (3) the use of population abundances that are strongly influenced by lag effects and drift to estimate immediate responses to the environment and competition.
Moreover, interspecific competition may actually synchronize, rather than de-synchronize, population dynamics [@Loreau2008a; @Loreau2010].

@@

\noindent where $\sigma_{r_{i}}$ is the temporal variance of species *i*'s per capita population growth rate ($r_i$) and $\sigma^{2}_{T}$ is the temporal variance of the aggregate community-level growth rate. 
The metric of @Loreau2008a makes clear that synchrony and asynchrony are not binary states, contrary to their common usage in the literature.
Rather, the synchrony of community dynamics lies along a continuum from perfect asynchrony ($\phi_r=0$) to perfect synchrony ($\phi_r=1$).
Thus, our focus should not be on whether or not (a)synchronous dynamics occur, but instead on the degree of (a)synchrony within a community and what process increase or decrease sychrony.

@@

\noindent where $\sigma^{2}_{c}$ is the temporal variance of per capita population growth rates due to regulation of community size (density-dependence), $\sigma^{2}_{e}$ is environmental variance, and $\sigma^{2}_{d}$ is demographic variance. *S* is the species richness of the focal community and *N* is the harmonic temporal mean of either the entire community (no subscript in numerator) or species *i* (with subscript in denominator). 
Their analysis isolates three main factors that drive species synchrony in competitive communities: (1) density-dependence via intra- and interspecific competition, (2) environmental fluctuations, and (3) demographic stochasticity.

@@

### Demographic stochasticity decreases synchrony
In communities where environmental forcing and community regulation by inter and intraspecific density-dependence are weak, species should fluctuate independently and community synchrony is expected to equal the inverse of the number of species in the community (1/*S*).
Such independent fluctuations are expected for per capita growth rates regardless of population sizes, whereas synchrony of percent cover should trend toward one (perfect synchrony) as population sizes increase and the effect of demographic stochasticity is diminished.
Our results conform to expectations: for each community except Arizona, community synchrony of per capita growth rates are approximately equal to 1/*S* when only demographic stochasticity is acting (Fig. 3; top panels, dark purple lines) and synchrony of percent cover starts at approximately 1/*S* and increases linearly as population sizes increase (Fig. 3; bottom panels, dark purple lines).
In the Arizona community, synchrony of per capita growth rates is approximately 1/*S* as expected, but synchrony of precent cover does not increase with population size (Fig. 3f).
This could indicate that intraspecific density-dependence is abnormally strong in the Arizona community, relative to the other communities we studied.
Strong intraspecific density-dependence for the two species in the Arizona community would limit population size regardless of landscape size.
Therefore, populations would not grow large enough to limit the desynchronizing effect of demographic stochasticity.
In other words, if there is no relationship between landscape size and population size due to strong density-dependence, the effect of demgographic stochasticity will not lessen.
\todo[inline, size=\small]{CHECK MEAN COVER VERSUS LANDSCAPE SIZE FOR EACH COMMUNITY}

@@

### Environmental fluctuations drive community synchrony
In large populations where interspecific interactions are weak, synchrony is expected to be driven exclusively by environmental fluctuations.
Under such conditions community synchrony should approximately equal the synchrony of species' responses to the environment.
We find that environmental fluctuations drive synchrony of per capita growth rates and plant percent cover in all five communities.
Removing environmental fluctuations consistently reduced synchrony (Fig. 3) and the synchrony of species environmental responses was a strong predictor of community synchrony ($\text{R}^2$ = 0.67; Fig. 4).
Likewise, removing interspecific interactions resulted in no discernable change in community synchrony of per capita growth rates (Fig. 2).
The lack of change indicates a strong correlation between species growing in polyculture (with interspecific interactions) and in monoculture (without interspecific interactions).
If we consider sychrony in monoculture to represent the synchrony of species' responses to the environment, then our results lead to only one conclusion: environmental fluctuations are the primary driver of community synchrony.
This is unsurprising since we know that species interactions are weak in these communities.
More surprising is that our results appear to be quite general: across five arid-to-subhumid grasslands community synchrony is almost soley due to environmental fluctuations since interspecific interactions are weak.
Given accumulating evidence that niche differences in natural communities are large [reviewed in @Chu2015], and thus species interactions are likely to be weak, our results are likely very general when applied to natural grasslands.

A challenge to generality of our results is that a recent analysis of several biodiversity-ecosystem function experiments suggests our results may be anomolous.
@Gross2014 found that temporal asynchrony among plant species in four experiments was driven by interspecific competition that counteracted the synchronizing effect of environmental fluctuations.
This is surprising given the extremely weak species interactions we estimated.
But the apparent inconsistency between our results and those of @Gross2014 disappears when we consider the differences between our studies.
Gross et al.'s results are based on experimentally-assembled communities that have coexisted for, at most, 11 years.
In contrast, the natural communities we studied consist of species that have coexisted for decades and have virtually zero niche overlap [@Chu2015].
In theory, species interactions should weaken through time as community assembly progesses [@Kokkoris1999], meaning that in biodiversity-ecosystem function experiments community assembly processes that can result in competitive exclusion may yet to have been realized.
Therefore, such communities may be highly influenced by transient, but strong, interspecific competition that can mask the synchronizing effects of the environment.
This also leads to the prediction that community synchrony is driven by competition in recently assembled communities, while synchrony is driven by environmental fluctuations in communities that have undergone extensive species sorting.
In other words, in the absence of disturbance and invasion, the dominant driver of community synchrony should shift from competition to environmental fluctuations through time.
One way to test this prediction is to continue collecting data from biodiversity-ecoystem function experiments and conduct the analysis of @Gross2014 every few years.

The generality of our results only extends to communities composed of a single trophic level. \textcolor{red}{DO WE NEED THIS?}

Our analysis also contributes to mounting evidence on the importance of functional diversity for maintaining temporal stability via species asynchrony [@Reich2012; @Polley2013].
Functional traits define how a species will respond to its environment.
Therefore, greater functional differences among species should lead to lower correlations in species' responses to the environment.
We found evidence for the negative effect of functional diversity on community synchrony: community synchrony was lowest Idaho (Table 2, Fig. 2); the only community that contained two life forms (one shrub, three perennial grasses).
In fact, when we ran simulations with the shrub removed, synchrony of the Idaho community increased substantially and was similar to synchrony in the Kansas community, which also contained three species.
Functional diversity is especially important in communities with weak interspecific interactions where synchrony depends soley on species' environmental responses.
Adding species to such communities will always decrease synchrony, and increase temporal stability, so long as the synchrony of species' environmental response is less than 1 [@Loreau2008a; @Loreau2013].
But functionally diverse suites of species will have the lowest synchrony of environmental responses, and thus lowest community synchrony and highest stability.

Conclusion
----------
We used empirically-based, multi-species population models to test predictions arising from theory on the drivers of species synchrony.
Our results show that community-wide synchrony is predominantly driven by environmental forcing across five perennial plant communities.
Thus, our results support Loreau and de Mazancourt's (2008) prediction that community-wide synchrony of per capita growth rates should approximately equal the synchrony of species' environmental responses when demographic stochasticity and species interactions are weak.
We have reason to believe that our results are quite general since many studies report strong niche differences in plant communities; meaning that species interactions are weak.
However, our results are in contrast to a recent analysis of several biodiversity-ecosystem function experiments showing that competition drives community synchrony.
We conclude that the difference between the Gross et al. (2014) study and our own is due to community assembly processes: recently assembled communities, such as experimental plots, may exhibit strong species interactions that will weaken over time [@Kokkoris1999].
Viewing community synchrony through the lens of community assembly processes may provide a way to reconcile inconsistent observations on the biotic and abiotic forces that jointly drive community dynamics.

@@

\setlength{\parindent}{0ex}
\newpage{}

@@

pgr_plot <- ggplot(data=pgr_data, aes(x=(year+1900), y=pgr, color=color))+
              geom_line(alpha=0.25)+
                geom_point(size=2)+
              facet_grid(site~.)+
              guides(color=FALSE)+
              ylab("Per Capita Growth Rate")+
              xlab("Year")+
              scale_color_manual(values = brewer.pal(12,"Paired"))+
              theme_bw()
full_plot <- grid.arrange(cover_plot, pgr_plot, ncol=2)
```
